Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Minor formatting change
Remove comment stuff related to Hspec
whitespace change

\authorinfo{Simon HENGEL}
           {}
           {sol@typeful.net}
%% \authorinfo{Trystan SPANGLER}
%%            {TBD: Affiliation}
%%            {TBD: Email}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

\begin{quote}
\emph{NOTE: @sol has to release a new version of hspec, that includes
the Spec-to-Specs and hspecX-to-hspec changes.  Otherwise the code in
this paper will not work!}
\end{quote}

@@

\item
    Introduce a set of combinators to set expectations about \emph{code
    examples} for use with \hspec{}.
%% \item Introduced {\tt Hspec} from Ruby community to Haskell community and
%% integrated it with QuickCheck
%% (Section \ref{sec:for-developers} and Section \ref{sec:hspec})
\item Show best current practice of BDD in Haskell using \doctest{} and
    \hspec{} (Section \ref{ref:Best-current-practice})
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \subsection{Hspec}
%% \label{sec:hspec}

%% TBD.

>>>>

\authorinfo{Simon HENGEL}
           {}
           {sol@typeful.net}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

\emph{IMPORTANT: @sol has to release a new version of hspec, that
includes the Spec-to-Specs and hspecX-to-hspec changes.  Otherwise the
code in this paper will not work!}

@@

\item
    Introduce a set of combinators to set expectations about
    \emph{code examples} for use with \hspec{}.

\item
    Show best current practice of BDD in Haskell using \doctest{} and
    \hspec{} (Section \ref{ref:Best-current-practice})

\end{itemize}

@@
